How cryptic is cryptic diversity? \newline Machine learning approaches to fine scale variation in the morphology of \textit{Emys marmorata}.

### 2013-06-18 documents/turtle_presentation.Rnw
pretty wireframes

ex.lab <- function(var, value) {
  value <- as.character(value)
  if(var == 'lab') {
    value[value == '1'] <- 'min'
    value[value == '2'] <- 'max'
  }
  return(value)
}

fst.mean <- multishape.plot(list(turtle.land.adult[, , fst.min], 
                                 turtle.land.adult[, , fst.max]), 
                            links = links,
                            labeller = ex.lab)
fst.mean <- fst.mean + theme(axis.title = element_blank(),
                             axis.text = element_text(size = 5))
fst.mean
@

@@

snd.mean <- multishape.plot(list(turtle.land.adult[, , snd.min], 
                                 turtle.land.adult[, , snd.max]), 
                            links = links,
                            labeller = ex.lab)
snd.mean <- snd.mean + theme(axis.title = element_blank(),
                             axis.text = element_text(size = 5))
snd.mean
@
\end{frame}

>>>>

ex.lab <- function(var, value) {
  value <- as.character(value)
  if(var == 'lab') {
    value[value == '1'] <- 'min'
    value[value == '2'] <- 'mean'
    value[value == '3'] <- 'max'
  }
  return(value)
}

fst.mean <- multishape.plot(list(turtle.land.adult[, , fst.min], 
                                 mt,
                                 turtle.land.adult[, , fst.max]), 
                            links = links,
                            labeller = ex.lab)
fst.mean <- fst.mean + theme(axis.title = element_blank(),
                             axis.text = element_text(size = 4))
fst.mean <- fst.mean + coord_equal()
fst.mean
@

@@

snd.mean <- multishape.plot(list(turtle.land.adult[, , snd.min], 
                                 mt,
                                 turtle.land.adult[, , snd.max]), 
                            links = links,
                            labeller = ex.lab)
snd.mean <- snd.mean + theme(axis.title = element_blank(),
                             axis.text = element_text(size = 4))
snd.mean <- snd.mean + coord_equal()
snd.mean
@
\end{frame}
